---
title: "State Freight and Econ Profile"
date: "Last Update: 2023-12-02"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(sf)
library(tmap)
tmap_mode("view")
library(tigris)
library(tidycensus)
library(censusapi)
library(ggplot2)
library(plotly)
library(scales)
library(ggspatial)
library(arcpullr)
library(base)
library(basemaps)

#counties <- c("Anoka", "Carver", "Chisago", "Dakota", "Hennepin", "Ramsey", "Scott", "Washington")

FreightNAICS <- c("11", "21", "22", "23", "31", "32", "33", "31-33", "42", "44", "45", "44-45", "48", "49", "48-49", "72")

# MnDOT Color Schemes
# https://mn.gov/portal/brand/style-guide/colors/
mycols <- list(
  colBlue  = "#003865",
  colGreen = "#78BE21",
  colWhite = "#FFFFFF",
  colBlack = "#000000",
  colAcTeal = "#008EAA",
  colAcGreen = "#0D5257",
  colAcOrange = "#8D3F2B",
  colAcPurple = "#5D295F",
  colAcBlueGray = "#A4BCC2",
  colAcCream = "#F5E1A4",
  colAcSkyBlue = "#9BCBEB",
  colAcGold = "#FFC845",
  colDarkGray = "#53565A",
  colMedGray = "#97999B",
  colLightGray = "#D9D9D6",
  colSafeRed = "#A6192E",
  colSafeOrange = "#E57200"
)

crs <- 6505
basemaps <- tm_basemap(c("CartoDB.Positron", "OpenStreetMap.Mapnik", "Esri.WorldImagery"))

countiesSF <- 
  counties(state = "MN", cb = TRUE, progress_bar = FALSE) %>% 
  #filter(NAME %in% counties) %>% mutate(metro = TRUE) %>% 
  st_transform(crs)

study_boundary <- countiesSF %>% summarize()
study_boundary %>% write_sf("ArcMap/forGIS/StudyBoundary.shp")


basetile <- basemap(
  ext = countiesSF %>% filter(metro = TRUE) %>% st_buffer(5280*1), 
  map_service = "carto", map_type = "light"
  )

tmap_mode("plot")
tm_shape(basetile) + tm_rgb()
#tmap_mode("view")


# Function Definitions
read_sf_zipM <- function(path) {   
  temp <- tempfile()   
  temp2 <- tempfile()   
  download.file(path, temp)   
  unzip(zipfile = temp, exdir = temp2)   
    
  filenames <- list.files(temp2, recursive = TRUE, pattern = glob2rx("*.shp"), full.names = TRUE)  
  filenamesAbb <- list.files(temp2, recursive = TRUE, pattern = glob2rx("*.shp"))  
  filenum <- length(filenames)  
    
  x <- list()  
   
  for (i in 1:filenum) {  
    x[[i]] <- read_sf(filenames[i])  
  }  
    
  names(x) <- filenamesAbb  
    
  x  
}

read_sf_zip <- function(path) { 
    temp <- tempfile() 
    temp2 <- tempfile() 
    download.file(path, temp) 
    unzip(zipfile = temp, exdir = temp2) 
    read_sf(temp2) 
}


save(
  counties,
  study_boundary,
  mycols,
  crs,
  basemaps,
  read_sf_zip,
  read_sf_zipM,
  file = "base_data.rdata"
)

```



-   ...

# Population Data

```{r}

totPop <- 
  get_acs(
    "block group", variables = c("B01001_001"), output = "tidy", 
    state = "MN", geometry = TRUE, year = 2021
    ) %>%
  st_transform(crs) %>%
  mutate(
    area = st_area(.), 
    areaSM = area %>% units::set_units(mi^2),
    popDensity = estimate/area)

totPop %>% write_sf("ArcMap/forGIS/PopulationDensity.shp")

popTract2021 <- 
    get_acs(
    "county", variables = c("B01001_001"), output = "tidy", 
    state = "MN", geometry = TRUE, year = 2021
    ) %>%
  mutate(estimate2021 = estimate) #%>% 
  st_transform(crs)


popTract2021 %>% st_is_valid()
basemaps +
  tm_shape(popTract2021) + tm_polygons()

popTract2016 <-
    get_acs(
    "county subdivision", variables = c("B01001_001"), output = "tidy", 
    state = "MN", geometry = TRUE, year = 2016
    ) %>%
  st_transform(crs) %>%
  mutate(estimate2016 = estimate)
  

# Need to do a spatial join since the GEOIDs changed a bit between 2016 and 2021
popTract2021Centroid <- popTract2021 %>% st_point_on_surface()
popTract2016Centroid <- popTract2016 %>% st_point_on_surface()

popTractXwalk <- 
  popTract2021 %>% st_join(popTract2016Centroid) %>% 
  select(
    GEOID2016 = GEOID.y,
    GEOID2021 = GEOID.x,
    pop2016 = estimate.y,
    pop2021 = estimate.x
    ) %>% 
  group_by(GEOID2021) %>% 
  summarize(
    pop2016 = sum(pop2016),
    pop2021 = first(pop2021)
  ) 

basemaps +
  tm_shape(popTract2021Centroid) + tm_dots()

# Manual Adjustment for some areas that didn't line up well
popTractXwalk[popTractXwalk$GEOID2021 == "2705315148", 2] <- 4296
popTractXwalk[popTractXwalk$GEOID2021 == "2705315148", 3] <- 4367

popTractXwalk <- 
  popTractXwalk %>%
  mutate(
    percChange = (pop2021 - pop2016) / pop2016,
    change = pop2021 - pop2016
    )

basemaps +
  tm_shape(popTract2016) + tm_polygons(alpha = 0.5) +
  tm_shape(popTract2021) + tm_polygons(alpha = 0.5)

popTractChange <- 
  popTract2016 %>% 
  left_join(popTractXwalk %>% st_drop_geometry(), by = c("GEOID" = "GEOID2021"))

popTractChange %>% write_sf("ArcMap/forGIS/PopulationChange.shp")

basemaps +
  tm_shape(popTractChange) + tm_fill(col = "change", alpha = 0.8, palette = "Spectral", popup.vars = TRUE, style = "fixed", breaks = c(-10000, -5000, 0, 5000, 10000, 25000))

tmap_mode("view")
basemaps +
  tm_shape(popTract2016) + tm_borders(col = "red", lwd = 5) +
  tm_shape(popTract2021) + tm_borders() + tm_dots()


# Total Population Change

pop2021 <- 
    get_acs(
    "county", variables = c("B01001_001"), output = "tidy", 
    state = "MN", county = counties, geometry = FALSE, year = 2021
    ) %>% summarize(pop2021 = sum(estimate)) %>% pull(pop2021)

pop2016 <- 
    get_acs(
    "county", variables = c("B01001_001"), output = "tidy", 
    state = "MN", county = counties, geometry = FALSE, year = 2016
    ) %>% summarize(pop2016 = sum(estimate)) %>% pull(pop2016)

pop2021 - pop2016

pop2021 / pop2016

```

# Economic Profile

The District 6 Freight Plan is designed to identify and prioritize freight projects that support the economy of southeastern Minnesota. To do so, it is important to understand the region's economy and the role that freight plays in supporting it. This information provides a foundation for further discussions of freight transportation needs and issues in the District.

## Minnesota and the Metro District Economy

```{r echo = FALSE, warning = FALSE, message = FALSE}
# BEA Data downloaded from: https://apps.bea.gov/regional/downloadzip.cfm
# Much of the BEA data represents combinations of different industry categories
# This filters to the lowest denominator as well as "Gov" and "All" categories
beaMN <- read_csv("Tables/CAGDP2_MN_2001_2021.csv") %>%
  mutate(IndustryClassification = case_when( 
    Description == "All industry total" ~ "All",
    Description == "Government and government enterprises" ~ "Gov",
    TRUE ~ IndustryClassification
  )) %>%
  filter(IndustryClassification %in% c("All", "Gov", "11", "21", "22", "23", "31-33", "42", "44-45", "48-49", "51", "52", "53", "54", "55", "56", "61", "62", "71", "72", "81")) %>%
  mutate(
    GEOID = as.character(GeoFIPS),
    across(`2001`:`2021`, ~as.numeric(.)),
    FreightRel = case_when(
      IndustryClassification %in% FreightNAICS ~ TRUE,
      TRUE ~ FALSE
    )) %>%
  pivot_longer(cols = `2001`:`2021`, names_to = "Year", values_to = "Thousands") %>%
  left_join(
    countiesSF %>% st_drop_geometry() %>% select(GEOID, metro)
    ) %>%
  mutate(MissingData = case_when(
    is.na(Thousands) ~ TRUE,
    TRUE ~ FALSE
  )) %>%
  group_by(Description, GeoFIPS) %>% 
  mutate(avg = mean(Thousands, na.rm = TRUE)) %>% 
  ungroup() %>%
  mutate(
    Thousands = case_when(
      MissingData == TRUE ~ avg,
      MissingData == FALSE ~ Thousands)
    ) 

naicsName = beaMN %>% group_by(IndustryClassification, Description) %>% summarize() %>%
  bind_cols(shortname = c(
    "11: Agriculture",
    "21: Mining/Quarrying",
    "22: Utilities",
    "23: Construction",
    "31-33: Manufacturing",
    "42: Wholesale Trade",
    "44-45: Retail Trade",
    "48-49: Transportation",
    "51: Information",
    "52: Finance/Insurance",
    "53: Real Estate",
    "54: Prof. Services",
    "55: Company Management",
    "56: Admin./Support",
    "61: Educational Services",
    "62: Health Care/Soc. Services",
    "71: Arts/Recreation",
    "72: Accomm./Food Services",
    "81: Other Services",
    "All Industry Total",
    "Government"
  )) %>% mutate(NAICS2 = str_sub(shortname, 1, 2))

beaMN <- beaMN %>% left_join(naicsName)
  
beaMNall <- beaMN %>% filter(IndustryClassification != "All", GeoName == "Minnesota")
beaMNmetro <- beaMN %>% filter(IndustryClassification != "All", metro == TRUE)
```

**Figure X: Minnesota GDP by Industry**

```{r echo = FALSE, warning = FALSE, message = FALSE}
#### Chart of GDP by Industry for MN ####
beaMNall %>%
ggplot(aes(x = Year, y = Thousands/1000000, 
           fill = factor(FreightRel, levels = c(TRUE, FALSE)))) + 
  geom_col(col = NA) +  
  scale_fill_manual(name = element_blank(),
                  values = c( #assign legend colors
                      mycols$colBlue,
                      mycols$colGreen),
                  labels = c( #assign legend labels
                      "TRUE" = "Freight Related",
                      "FALSE" = "Not Freight Related"
                      )) +
  theme(
    strip.background = element_rect(fill = mycols$colAcBlueGray),
    strip.text = element_text(hjust = 0, size = 9),
    panel.background = element_rect(fill = "gray95"),
    panel.grid.major = element_line(color = "gray80", size = 0.15),
    axis.text.x = element_text(angle = 90, vjust = 0.4, size = 7),
    axis.text.y = element_text(size = 6),
    legend.position = "top",
    legend.text = element_text(size = 8),
  ) +

  labs(
    y = "Gross Domestic Product ($Billions)"
    ) +
  facet_wrap(~shortname)
  
ggsave("Plot/GDP_MN.png", width = 10, height = 6.5, dpi = 300)
```

**Figure X: Metro District GDP by Industry**

```{r echo = FALSE, warning = FALSE, message = FALSE}
#### Chart of GDP by Industry for D6 ####
beaMNmetro %>%
ggplot(aes(x = Year, y = Thousands/1000000, 
           fill = factor(FreightRel, levels = c(TRUE, FALSE)))) + 
  geom_col(col = NA) +  
  scale_fill_manual(name = element_blank(),
                  values = c( #assign legend colors
                      mycols$colBlue,
                      mycols$colGreen),
                  labels = c( #assign legend labels
                      "TRUE" = "Freight Related",
                      "FALSE" = "Not Freight Related"
                      )) +
  theme(
    strip.background = element_rect(fill = mycols$colAcBlueGray),
    strip.text = element_text(hjust = 0, size = 9),
    panel.background = element_rect(fill = "gray95"),
    panel.grid.major = element_line(color = "gray80", size = 0.15),
    axis.text.x = element_text(angle = 90, vjust = 0.4, size = 7),
    axis.text.y = element_text(size = 6),
    legend.position = "top",
    legend.text = element_text(size = 8),
  ) +

  labs(
    y = "Gross Domestic Product ($Billions)"
    ) +
  facet_wrap(~shortname)
  
ggsave("Plot/GDP_Metro.png", width = 10, height = 6.5, dpi = 300)

```

**Figure X: Percent of 2019 GDP by Industry**

```{r echo = FALSE, warning = FALSE, message = FALSE}
beaMN_2021 <- beaMN %>% filter(Year == "2021", GeoName == "Minnesota") %>%
  mutate(totGDP = .$Thousands[.$IndustryClassification == "All"],
         percGDPlabel = percent(Thousands / totGDP, accuracy = 0.1),
         percGDP = -Thousands / totGDP,
         area = "Minnesota")

beaMetro_2021 <- beaMN %>% filter(Year == "2021", metro == TRUE) %>%
  group_by(IndustryClassification, shortname, FreightRel) %>% summarize(Thousands = sum(Thousands, na.rm = TRUE)) %>%
  mutate(totGDP = .$Thousands[.$IndustryClassification == "All"],
         percGDP = case_when(
           is.na(Thousands) ~ 0,
           TRUE ~ Thousands / totGDP
           ),
         percGDPlabel = percent(Thousands / totGDP, accuracy = 0.1),
         area = "District 6"
  )

beaCombo <- bind_rows(beaMN_2021, beaMetro_2021) %>% filter(shortname != "All Industry Total")

# Comparison Chart of percent of GDP in each Industry
ggplot(beaCombo, aes(x = fct_rev(shortname), y = percGDP, 
                     fill = factor(interaction(FreightRel, area),
                                   levels = c(
                                     "TRUE.District 6",
                                     "FALSE.District 6",
                                     "TRUE.Minnesota",
                                     "FALSE.Minnesota"
                                   )))) + 
  geom_col() +
  coord_flip() +
  scale_fill_manual(name = element_blank(), 
                  values = c( #assign legend colors 
                      "TRUE.District 6" = alpha(mycols$colBlue, 1), 
                      "FALSE.District 6" = alpha(mycols$colGreen, 1),
                      "TRUE.Minnesota" = alpha(mycols$colBlue, 0.5), 
                      "FALSE.Minnesota" = alpha(mycols$colGreen, 0.5) 
                       ), 
                  labels = c( #assign legend labels 
                      "Freight Related", 
                      "Not Freight Related"
                      ), 
                  breaks = c( #include only the solid color legend items
                    "TRUE.District 6",
                    "FALSE.District 6"
                  )) +
  geom_text(data = beaCombo %>% filter(percGDP>0), 
            aes(label = percGDPlabel), hjust = 0, vjust = 0.4, nudge_y = 0.005, size = 2) +
  geom_text(data = beaCombo %>% filter(percGDP<=0), 
            aes(label = percGDPlabel), hjust = 1, vjust = 0.4, nudge_y = -0.005, size = 2) +
  geom_text(aes(x = 20, y = 0.08, hjust = 0, label = "Metro Industries"), 
                size = 3, fontface = "bold", color = mycols$colDarkGray) +
  geom_text(aes(x = 20, y = -0.08, hjust = 1, label = "Statewide Industries"), 
                size = 3, fontface = "bold", color = mycols$colDarkGray) +
  labs(
    y = "Percent GDP",
    x = "Industry"
    ) +
  theme(
    legend.position = "top",
    
    ) +
  scale_y_continuous(labels = function(x) scales::percent(abs(x)), limits = c(-0.2, 0.25))

ggsave("Plot/GDP_Metro_2021Breakdown.png", width = 6.5, height = 4, dpi = 300)



    
```

**Figure X: Metro GDP as proportion of Statewide Total**

```{r}


beaMetro_2021 %>%
  select(IndustryClassification, shortname, FreightRel, totGDPmetro = Thousands) %>% 
  left_join(beaMN_2021 %>% select(shortname, Thousands), by = "shortname") %>% 
  mutate(
    percStatewide = totGDPmetro / Thousands, 
    area = "metro",
    label = round(percStatewide * 100, 1)) %>% 
  arrange(desc(percStatewide)) %>% 
  ggplot(aes(x = fct_reorder(shortname, percStatewide), y = percStatewide,
             fill = factor(FreightRel, levels = c(TRUE, FALSE)))) +
  geom_col() +
  coord_flip() +
  scale_fill_manual(name = element_blank(), 
                  values = c( #assign legend colors 
                      alpha(mycols$colBlue, 1), 
                      alpha(mycols$colGreen, 1)
                      ), 
                  labels = c( #assign legend labels 
                      "Freight Related", 
                      "Not Freight Related"
                      )
                  ) +
  geom_text(aes(label = label), hjust = 0, vjust = 0.4, nudge_y = 0.005, size = 2) +
  labs(
    y = "Percent of Statewide GDP",
    x = "Industry"
    ) +
  theme(
    legend.position = "top",
    
    ) +
  scale_y_continuous(labels = function(x) scales::percent(abs(x)), limits = c(0, 1))
  

ggsave("Plot/MetroGDPofState.png", width = 6.5, height = 4, dpi = 300)

```

# Employment

### Census Business Pattern Data Analysis

```{r}
Sys.setenv(CENSUS_KEY = "f3a45e01dd57821ead6ebefeb8e27670f4b474ea")

# CBP Data Analysis
empData2021 <- getCensus(
  name = "2021/cbp",
  vars = c("COUNTY", "EMP", "EMPSZES", "EMPSZES_LABEL", "ESTAB", "NAICS2017", "YEAR", "PAYANN"),
  region = "county:*", 
  regionin = "state:27")

# Summarize Employment and Establishment data
empDataMetro <- empData2021 %>%
  mutate(
    NAICS = case_when( #Rename the ranged NAICS Codes 
      NAICS2017 == "31-33" ~ "31",
      NAICS2017 == "44-45" ~ "44",
      NAICS2017 == "48-49" ~ "48",
      TRUE ~ NAICS2017),
    len = nchar(NAICS), #Define the length of the NAICS codes
    EMP = as.numeric(EMP),
    ESTAB = as.numeric(ESTAB),
    PAYANN = as.numeric(PAYANN),
    FreightRelated = case_when( #Define whether the NAICS codes are freight or non-freight related
      NAICS %in% FreightNAICS ~ "Freight",
      TRUE ~ "Non-Freight"
    )
  ) %>%
  filter(
    COUNTY %in% countiesSF$COUNTYFP, #Filter to only include target counties
    len <= 2, # Include 2, 3, and 4 digit NAICS codes
    EMPSZES == "001", #Exclude establishment employee size bins, include only "all establishments"
    !NAICS %in% c("00", "99") #Exclude "All Industry" and unknown outliers
  ) %>%
  select(-EMPSZES_LABEL, -EMPSZES) %>%
  group_by(NAICS, YEAR, FreightRelated) %>%
  summarize(emp = sum(EMP), estab = sum(ESTAB), year = first(YEAR), pay = sum(PAYANN)) %>%
  left_join(naicsName, by = c("NAICS" = "NAICS2"))
  
empDataMetro %>% group_by(FreightRelated) %>% summarize(emp = sum(emp), estab = sum(estab), pay = sum(pay))

# Freight-related employment as a proportion of all employment
empDataMetro %>% filter(FreightRelated == "Freight") %>% group_by(YEAR) %>% summarize(sum(emp)) %>% pull() / empDataMetro %>% group_by(YEAR) %>% summarize(sum(emp)) %>% pull()
```

### LEHD Data Analysis

```{r}

#LEHD Analysis

#Download data for Workplace characteristics, All Jobs
#Sum to block group level and sum for All Jobs and Freight NAICS Jobs
mn_wac_AllJobs_2020 <- read_csv("https://lehd.ces.census.gov/data/lodes/LODES8/mn/wac/mn_wac_S000_JT00_2021.csv.gz",
                                col_types = cols(w_geocode = col_character())) %>%
  mutate(BG = str_sub(w_geocode, 1, 12)) %>%
  group_by(BG) %>%
  summarize(
    numBlocks = n(),
    NAICS_All = sum(C000), #perc_All = NAICS_All / NAICS_All,
    NAICS_11 = sum(CNS01), #perc_11 = NAICS_11/NAICS_All,
    NAICS_21 = sum(CNS02), #perc_21 = NAICS_21/NAICS_All,
    NAICS_22 = sum(CNS03), #perc_22 = NAICS_22/NAICS_All,
    NAICS_23 = sum(CNS04), #perc_23 = NAICS_23/NAICS_All,
    NAICS_31 = sum(CNS05), #perc_31 = NAICS_31/NAICS_All,
    NAICS_42 = sum(CNS06), #perc_42 = NAICS_42/NAICS_All,
    NAICS_44 = sum(CNS07), #perc_44 = NAICS_44/NAICS_All,
    NAICS_48 = sum(CNS08), #perc_48 = NAICS_48/NAICS_All,
    NAICS_51 = sum(CNS09),
    NAICS_52 = sum(CNS10),
    NAICS_53 = sum(CNS11),
    NAICS_54 = sum(CNS12),
    NAICS_55 = sum(CNS13),
    NAICS_56 = sum(CNS14),
    NAICS_61 = sum(CNS15),
    NAICS_62 = sum(CNS16),
    NAICS_71 = sum(CNS17),
    NAICS_72 = sum(CNS18), #perc_72 = NAICS_72/NAICS_All,
    NAICS_81 = sum(CNS19),
    NAICS_92 = sum(CNS20),
    NAICS_All = sum(C000),
    FreightEmp = sum(CNS01, CNS02, CNS03, CNS04, CNS05, CNS06, CNS07, CNS08),
    GoodsProdEmp = sum(CNS01, CNS02, CNS04, CNS05),
    FreightProp = FreightEmp / NAICS_All,
    GoodsProp = GoodsProdEmp / NAICS_All
  ) %>%
  mutate(GEOID = str_sub(BG, 1, 5)) %>%
  inner_join(countiesSF %>% select(GEOID, NAME)) %>%
  select(-geometry)

#mn_wac_AllJobs_2018 %>% summarize(across(NAICS_All:GoodsProdEmp, ~ sum(.))) %>% write_csv("temp.csv")

FreightJobsSF <- 
  block_groups("MN", county = counties, cb = TRUE) %>% 
  left_join(mn_wac_AllJobs_2020, by = c("GEOID" = "BG")) %>% 
  st_transform(crs) %>% 
  mutate(sqmi = st_area(.) %>% units::set_units(mi^2)) %>% 
  mutate(
    FreightEmpDens = FreightEmp / sqmi,
    FreightEmpProp = FreightEmp / NAICS_All
    )

tmap_mode("view")
basemaps +
  tm_shape(
    FreightJobsSF %>% filter(as.numeric(FreightEmpDens) >= 1000) %>% 
      arrange(desc(NAICS_48)) %>% head(45)) + 
  tm_fill(col = "NAICS_48", style = "jenks", popup.vars = TRUE, alpha = 0.5)

FreightJobsSF %>% write_sf("ArcMap/forGIS/FreightEmp.shp")

  

```

# Location Quotions Function and Analysis

```{r}
NAICSdesc <- readxl::read_excel("data/2017_NAICS_Descriptions.xlsx") %>% 
  mutate(
    Title = case_when(
      str_sub(Title, -1,-1) == "T" ~ str_sub(Title, 1,-2),
      TRUE ~ Title
  )
)


Sys.setenv(CENSUS_KEY = "f3a45e01dd57821ead6ebefeb8e27670f4b474ea")
LQfunc <- function(naicsDig) {

    naicsLev <- naicsDig
    
    # Download US Employment by 3-dig NAICS
    EcSp3digUS <- getCensus(
      name = "2021/cbp",
      vars = c("EMP", "EMPSZES", "EMPSZES_LABEL", "ESTAB", "NAICS2017", "YEAR"),
      region = "us:*", 
      ) %>% 
      mutate(
        NAICS = case_when( #Rename the ranged NAICS Codes 
          NAICS2017 == "31-33" ~ "31",
          NAICS2017 == "44-45" ~ "44",
          NAICS2017 == "48-49" ~ "48",
          TRUE ~ NAICS2017),
        len = nchar(NAICS), #Define the length of the NAICS codes
        EMP = as.numeric(EMP),
        ESTAB = as.numeric(ESTAB),
        geo = "US"
      ) %>%
      filter(
        EMPSZES == "001",
        NAICS == "00" | len == naicsLev
        ) %>%
      mutate(denom = .$EMP[NAICS == "00"]) %>% select(EMP, NAICS, geo, denom)
    
    
    # Download D6 Employment by 3-dig NAICS
    EcSp3digD6 <- getCensus(
      name = "2021/cbp",
      vars = c("EMP", "EMPSZES", "EMPSZES_LABEL", "ESTAB", "NAICS2017", "YEAR"),
      region = "county:*",
      regionin = "state:27"
      ) %>% 
      mutate(
        NAICS = case_when( #Rename the ranged NAICS Codes 
          NAICS2017 == "31-33" ~ "31",
          NAICS2017 == "44-45" ~ "44",
          NAICS2017 == "48-49" ~ "48",
          TRUE ~ NAICS2017),
        len = nchar(NAICS), #Define the length of the NAICS codes
        EMP = as.numeric(EMP),
        ESTAB = as.numeric(ESTAB),
        geo = "D6"
      ) %>%
      filter(
        county %in% countiesSF$COUNTYFP,
        EMPSZES == "001",
        NAICS == "00" | len == naicsLev
        ) %>%
      group_by(NAICS) %>%
      summarize(
        EMP = sum(EMP),
        NAICS = first(NAICS),
        geo = first(geo)
      ) %>%
      mutate(denom = .$EMP[NAICS == "00"]) %>% select(EMP, NAICS, geo, denom)
    
    EcSp3digD6 %>% filter(!NAICS %in% c("00", "99")) %>% 
      left_join(NAICSdesc, by = c("NAICS" = "Code")) %>%
      ggplot(aes(x = reorder(Title, EMP), y = EMP)) + geom_col() +
      coord_flip()
    
    
    LQ <- EcSp3digD6 %>% filter(!NAICS %in% c("00", "99")) %>%   
      left_join(EcSp3digUS, by = "NAICS") %>%
      left_join(NAICSdesc, by = c("NAICS" = "Code")) %>%
      mutate(
        LQ = (EMP.x / denom.x) / (EMP.y / denom.y),
        FreightRel = case_when(
          str_sub(NAICS, 1, 2) %in% FreightNAICS ~ "Freight",
          TRUE ~ "Non-Freight")
        ) 
    
    return(LQ)

}
```


Application of Location Quotient Function (2-Digit)
```{r}
LQfunc(2) %>% mutate(Title = case_when(
                NAICS == "31" ~ "Manufacturing",
                NAICS == "44" ~ "Retail Trade",
                NAICS == "48" ~ "Transportation",
                
                TRUE ~ Title
                        )
  ) %>%                                                              
  ggplot(aes(x = reorder(paste0(NAICS, ": ", Title),LQ), y = LQ, fill = FreightRel)) + 
  geom_col() + coord_flip() + scale_x_discrete(labels = label_wrap(60)) + xlab("NAICS Industry") +
  scale_fill_manual(values = c(mycols$colBlue, mycols$colAcTeal)) +
  theme(legend.position = "top", legend.title = element_blank()) +
  geom_hline(yintercept = 1, color = mycols$colGreen, lwd = 1.25) +
  scale_y_log10()

ggsave("Plot/EmploymentLQ_2dig.jpg", height = 4, width = 6, dpi = 300)
```



Application of Location Quotient Function (3-Digit)
```{r}
LQfunc(3) %>% mutate(Title = case_when(
                NAICS == "31" ~ "Manufacturing",
                NAICS == "44" ~ "Retail Trade",
                NAICS == "48" ~ "Transportation",
                
                TRUE ~ Title
                        )
  ) %>%
  filter(FreightRel == "Freight") %>% 
  arrange(desc(LQ)) %>% head(10) %>% 
  ggplot(aes(x = reorder(paste0(NAICS, ": ", Title),LQ), y = LQ, fill = FreightRel)) + 
  geom_col() + coord_flip() + scale_x_discrete(labels = label_wrap(60)) + xlab("NAICS Industry") +
  scale_fill_manual(values = c(mycols$colBlue, mycols$colAcTeal)) +
  theme(legend.position = "top", legend.title = element_blank()) +
  geom_hline(yintercept = 1, color = mycols$colGreen, lwd = 1.25) +
  scale_y_log10()

ggsave("Plot/EmploymentLQ_3digFreightOnly.jpg", height = 4, width = 6, dpi = 300)
```



Application of Location Quotient Function (4-Digit)
```{r}
LQfunc(4) %>% mutate(Title = case_when(
                NAICS == "31" ~ "Manufacturing",
                NAICS == "44" ~ "Retail Trade",
                NAICS == "48" ~ "Transportation",
                
                TRUE ~ Title
                        )
  ) %>%
  filter(FreightRel == "Freight") %>% 
  arrange(desc(LQ)) %>% head(10) %>% 
  ggplot(aes(x = reorder(paste0(NAICS, ": ", Title),LQ), y = LQ, fill = FreightRel)) + 
  geom_col() + coord_flip() + scale_x_discrete(labels = label_wrap(60)) + xlab("NAICS Industry") +
  scale_fill_manual(values = c(mycols$colBlue, mycols$colAcTeal)) +
  theme(legend.position = "top", legend.title = element_blank()) +
  geom_hline(yintercept = 1, color = mycols$colGreen, lwd = 1.25) +
  scale_y_log10()

ggsave("Plot/EmploymentLQ_4digFreightOnly.jpg", height = 4, width = 6, dpi = 300)
```
